ANOVAS para pruebas de robustez de la red

```{r}
library(ggplot2)
library(plyr)
library(scales)
library(BBmisc)
library(reshape2)
library(fmsb)
library(tidyverse)
library(ggplot2)
library(agricolae)
library(classInt)
library(DescTools)
library(lsmeans)
library(sjstats)
library(pwr)
setwd("~/Downloads")
```

```{r}
setwd("~/Downloads")
d0=read.csv("coefs0b.txt", header= FALSE) #10,000 ahora 200
d48=read.csv('coefs48b.txt', header= FALSE) #10, 000 ahora 200
d25=read.csv('coefs25.txt', header= FALSE) #200
d51=read.csv('coefs51.txt', header= FALSE) #200
d37=read.csv('coefs37.txt', header= FALSE) #200
d52=read.csv('coefs52.txt', header= FALSE) #200
d13=read.csv('coefs13.txt', header= FALSE) #200
d50=read.csv('coefs50.txt', header= FALSE) #200
#d4=read.csv('coefs4.txt', header= FALSE) 1
#d49=read.csv('coefs49.txt', header= FALSE) 1
d28=read.csv('coefs28.txt', header= FALSE) #200
d54=read.csv('coefs54.txt', header= FALSE) #200
d40=read.csv('coefs40.txt', header= FALSE) #200
d55=read.csv('coefs55.txt', header= FALSE) #200
d16=read.csv('coefs16.txt', header= FALSE) #200
d53=read.csv('coefs53.txt', header= FALSE) #200
```
Desviaciones estadnar para grafica
```{r}
sd(d0$V1)
sd(d48$V1)
sd(d25$V1)
sd(d51$V1)
sd(d37$V1)
sd(d52$V1)
sd(d13$V1)
sd(d50$V1)
sd(d28$V1)
sd(d54$V1)
sd(d40$V1)
sd(d55$V1)
sd(d16$V1)
sd(d53$V1)
```



ANOVAS entre parejas con y sin

```{r}
d0$hois<-"whithout"
d48$hois<-"with"
d0d48<-rbind(d0, d48)

#ANOVA
#con intervalos chicos
anova1 <- aov(V1 ~ hois, data=d0d48)
#summary(anova1)
anova(anova1)

anova_stats(anova1)

#TukeyHSD(anova1)
hola<-lsmeans(anova1, ~ hois, adjust="tukey")
multcomp::cld(hola, alpha=0.05, Letters=letters)

bartlett.test(V1 ~ hois, data=d0d48) #igualdad de varianzas. debe  ser no significativo
hist(residuals(anova1)) #debe ser normal
shapiro.test(residuals(anova1)) #normalidad, debe ser no significativo
par(mfrow=c(2,2)) # init 4 charts in 1 panel
plot(anova1)
```

```{r}
d25$hois<-"whithout"
d51$hois<-"with"
d25d51<-rbind(d25, d51)
d25d51$V1<-log10(max(d25d51$V1+1) - d25d51$V1)
d25d51
```
```{r}
#ANOVA
#con intervalos chicos
anova1 <- aov(V1 ~ hois, data=d25d51)
summary(anova1)
#anova(anova1)

anova_stats(anova1)

#TukeyHSD(anova1)
hola<-lsmeans(anova1, ~ hois, adjust="tukey")
multcomp::cld(hola, alpha=0.05, Letters=letters)

bartlett.test(V1 ~ hois, data=d25d51) #igualdad de varianzas. debe  ser no significativo
hist(residuals(anova1)) #debe ser normal
shapiro.test(residuals(anova1)) #normalidad, debe ser no significativo
par(mfrow=c(2,2)) # init 4 charts in 1 panel
plot(anova1)
```

```{r}
d37$hois<-"whithout"
d52$hois<-"with"
d37d52<-rbind(d37, d52)

#ANOVA
#con intervalos chicos
anova1 <- aov(V1 ~ hois, data=d37d52)
summary(anova1)
#anova(anova1)

anova_stats(anova1)

#TukeyHSD(anova1)
hola<-lsmeans(anova1, ~ hois, adjust="tukey")
multcomp::cld(hola, alpha=0.05, Letters=letters)

bartlett.test(V1 ~ hois, data=d37d52) #igualdad de varianzas. debe  ser no significativo
hist(residuals(anova1)) #debe ser normal
shapiro.test(residuals(anova1)) #normalidad, debe ser no significativo
par(mfrow=c(2,2)) # init 4 charts in 1 panel
plot(anova1)
```

```{r}
d13$hois<-"whithout"
d50$hois<-"with"
d13d50<-rbind(d13, d50)
#d13d50$V1<-log10(max(d13d50$V1+1) - d13d50$V1)

#ANOVA
#con intervalos chicos
anova1 <- aov(V1 ~ hois, data=d13d50)
summary(anova1)
#anova(anova1)

anova_stats(anova1)

#TukeyHSD(anova1)
hola<-lsmeans(anova1, ~ hois, adjust="tukey")
multcomp::cld(hola, alpha=0.05, Letters=letters)

bartlett.test(V1 ~ hois, data=d13d50) #igualdad de varianzas. debe  ser no significativo
hist(residuals(anova1)) #debe ser normal
shapiro.test(residuals(anova1)) #normalidad, debe ser no significativo
par(mfrow=c(2,2)) # init 4 charts in 1 panel
plot(anova1)
```

```{r}
d28$hois<-"whithout"
d54$hois<-"with"
d28d54<-rbind(d28, d54)

#ANOVA
#con intervalos chicos
anova1 <- aov(V1 ~ hois, data=d28d54)
summary(anova1)
#anova(anova1)
anova_stats(anova1)

#TukeyHSD(anova1)
hola<-lsmeans(anova1, ~ hois, adjust="tukey")
multcomp::cld(hola, alpha=0.05, Letters=letters)

bartlett.test(V1 ~ hois, data=d28d54) #igualdad de varianzas. debe  ser no significativo
hist(residuals(anova1)) #debe ser normal
shapiro.test(residuals(anova1)) #normalidad, debe ser no significativo
par(mfrow=c(2,2)) # init 4 charts in 1 panel
plot(anova1)
```

```{r}
d40$hois<-"whithout"
d55$hois<-"with"
d40d55<-rbind(d40, d55)

#ANOVA
#con intervalos chicos
anova1 <- aov(V1 ~ hois, data=d40d55)
summary(anova1)
#anova(anova1)

anova_stats(anova1)

#TukeyHSD(anova1)
hola<-lsmeans(anova1, ~ hois, adjust="tukey")
multcomp::cld(hola, alpha=0.05, Letters=letters)

bartlett.test(V1 ~ hois, data=d40d55) #igualdad de varianzas. debe  ser no significativo
hist(residuals(anova1)) #debe ser normal
shapiro.test(residuals(anova1)) #normalidad, debe ser no significativo
par(mfrow=c(2,2)) # init 4 charts in 1 panel
plot(anova1)
```

```{r}
d16$hois<-"whithout"
d53$hois<-"with"
d16d53<-rbind(d16, d53)

#ANOVA
#con intervalos chicos
anova1 <- aov(V1 ~ hois, data=d16d53)
summary(anova1)
#anova(anova1)

anova_stats(anova1)

#TukeyHSD(anova1)
hola<-lsmeans(anova1, ~ hois, adjust="tukey")
multcomp::cld(hola, alpha=0.05, Letters=letters)

bartlett.test(V1 ~ hois, data=d16d53) #igualdad de varianzas. debe  ser no significativo
hist(residuals(anova1)) #debe ser normal
shapiro.test(residuals(anova1)) #normalidad, debe ser no significativo
par(mfrow=c(2,2)) # init 4 charts in 1 panel
plot(anova1)
```
Cohen (1988) has provided benchmarks to define small (η2 = 0.01), medium (η2 = 0.06), and large (η2 = 0.14) effects.
https://www.frontiersin.org/articles/10.3389/fpsyg.2013.00863/full

Hattie states that an effect size of d=0.2 may be judged to have a small effect, d=0.4 a medium effect and d=0.6 a large effect on outcomes. He defines d=0.4 to be the hinge point, an effect size at which an initiative can be said to be having a 'greater than average influence' on achievement.
https://www.teachit.so/evidence.htm


ANOVAS entre emp con rand, small y scale. NO TIENE SENTIDO porque emp es solo un valor, no es muestra.
0,25,37,13
48,51,52,50

4,28,40,16
49,54,55,53
